Long name of the paper

### 2018-10-29 anzjs2018/sections/04_implementation.tex
cpu timings also

The primary concern is speed: 
we desire ETAs to be available as soon as possible after obtaining the data.
To do this, we use raw pointers to read-only GTFS objects,
and particles are only copied when resampling is required.
This is also why we chose to use protobuf as the output format,
since this is fast to write and distribute.
Steps 2b--e are performed in parallel, 
which in our test environment of a virtual machine with 8~cores, 
significantly speeds up computation.

As far as results, we have two categories:
implementation and faesibility,
and model performance;
we do not have any complex arrival time estimation method,
so no results for that are shown here.

The simulations we discuss here use a subset of real data from 8~October, 2018.
This allows us to run the model with different parameters over the same data.
The parameters varied were the number of particles and system noise $\sigma^2$.
The primary goal is to reduce the rate of degeneration and ``losing'' the bus 
(i.e., no particles are near the observed location),
and reducing the variance of parameter estimates; here we use vehicle speed as the example.

@@

During development of our application,
our primary concert was the computational faesibility of a particle filter.
For each iteration, 
the timings of the individual components in 2a--f above are recorded.
Since the number of vehicles traveling at any given time changes throughout the day,
we used the average timings from 13:45--14:00 to compare.

Figure~\ref{fig:timings} shows the timing results for varying number of particles.
Nothing too exciting going on here, 
except that writing ETAs takes up the largest chunk of time,
as this involves calculating quantiles which require the estimated ETAs to be sorted,
which is computationally demanding. 
The vehicle update takes the second longest time,
and involves copying particles during the update resampling step.
Finally, predicting the ETAs is pretty quick.
The remaining parts of the application take negligible time,
and all run on a single core to avoid mutex locks.

@@

>>>>

During the development of the application,
we were primarly concerned with ensuring each component of the program
is as efficient as possible,
allowing ETAs to be generated and distributed fast enough---our initial goal was 30~seconds.
Using \verb|C++| provides enough control over memory management
to ensure the program runs fast enough in \rt 
while still implementing the models.
We could also use OpenMP for parallelisation,
allowing us to process multiple vehicles simultaneously
depending on the number of cores available.

The particle filter requires thousands of particles per vehicle,
so it is necessary to explore the performance of the application
with varying number of particles.
It is also necessary to assess the performance of the particle filter,
and compare values for the fixed model parameters.
To do so, we implemented a simulated \rt environment
in which we could analyse the same subset of real vehicle data from 8~October, 2018
using a range of settings.
These simulations were carried out of a Virtual Machine 
with 8~cores and 32~Gb of memory, 
running Ubuntu~16.04 and using R~3.4.1.

@@

During development of our application,
our primary concert was the computational faesibility of a particle filter.
For each iteration, 
the timings of the individual components in 2a--f above are recorded.
Since the number of vehicles traveling at any given time changes throughout the day,
we used the average timings over a 15~minute window to compare.

Figure~\ref{fig:timings} shows the timing results for varying number of particles.
As expected,

Nothing too exciting going on here, 
except that writing ETAs takes up the largest chunk of time,
as this involves calculating quantiles which require the estimated ETAs to be sorted,
which is computationally demanding. 
The vehicle update takes the second longest time,
and involves copying particles during the update resampling step.
Finally, predicting the ETAs is pretty quick.
The remaining parts of the application take negligible time,
and all run on a single core to avoid mutex locks.

@@

The parameters varied were the number of particles,
GPS error $\epsilon$, and system noise $\sigma^2$.
The primary goal is to reduce the rate of degeneration and ``losing'' the bus 
(i.e., no particles are near the observed location),
and reducing the variance of parameter estimates; here we use vehicle speed as the example.
